|

### 2021-05-19 appendix/appendix.Rmd
add updated appendix

---
title: |
       | Supplementary Materials for "Casting the First Stone: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, <davidskarbek@brown.edu>, <http://davidskarbek.com>.

@@

This appendix contains the `R` code required to replicate the results we
present in "_Casting the First Stone: Understanding Attitudes towards Lynching
in Brazil_". This file also includes the descriptive statistics of our sample,
the average marginal component effects (AMCEs) for our conjoint experiment,
and additional subgroup analyses for all three experiments.

@@

# Load the dataset, remove unused rows and columns,
# and convert variable names to snake case
df <- read_csv("../data/data.csv") %>%
  clean_names() %>%
  mutate(response_id            = as.character(response_id),
         consent                = as.factor(q1),
         progress               = as.numeric(progress),
         finished               = as.factor(finished),
         age                    = as.numeric(q2),
         gender                 = as.factor(q3),
         race                   = as.factor(q4),
         education              = as.factor(q5),
         region                 = as.factor(q6),
         household_income       = as.factor(q7),
         ideology               = as.factor(q8),
         death_penalty          = as.factor(q9),
         previous_victim        = as.character(q10),
         previous_victim_text   = as.character(q10_text),
         views_police           = as.factor(q11),
         views_justice          = as.factor(q12),
         exp02_control          = as.numeric(q18),
         exp02_police           = as.numeric(q19),
         exp02_slow_justice     = as.numeric(q20),
         exp02_small_punishment = as.numeric(q21),
         exp03_control          = as.numeric(q22),
         exp03_constitution     = as.numeric(q23),
         exp03_rights           = as.numeric(q24),
         exp03_vendetta         = as.numeric(q25)) %>%
  slice(-1L) %>%
  select(-c(q1:q12, q18:q25)) %>%
  relocate(response_id, consent, progress, finished,
           location_latitude, location_longitude) %>%
  mutate(across(where(is.character), tolower)) %>%
  mutate(across(where(is.factor), tolower))

@@

In our first experiment, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

@@

\footnotesize
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ education),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School"))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)

@@

\footnotesize
```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
                                   views_police == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_police),
         views_police2 = fct_relevel(views_police2, "Very Good", "Good",
                                     "Regular", "Bad", "Very Bad")) %>%
  drop_na(views_police2)
cjdt$Police <- factor(cjdt$views_police2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)

@@

\footnotesize
```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
                                    views_justice == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_justice),
         views_justice2 = fct_relevel(views_justice2, "Very Good", "Good",
                                      "Regular", "Bad", "Very Bad")) %>%
  drop_na(views_justice2)
cjdt$Judiciary <- factor(cjdt$views_justice2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)

@@

\footnotesize
```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles"}
dfmat <- df1 %>%
  select(q13_text, q14_text, q15_text, q16_text, q17_text) %>%
  gather() %>%
  drop_na() %>%
  corpus(text_field = "value") %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE,
         remove_symbol = TRUE) %>%
  dfm() %>%
  dfm_remove(., pattern = c(stopwords("pt", source = "snowball"),
                            "é", "ser"))

@@

In our second experiment, we analyze how respondents justify their preferences
towards extralegal violence. We assess the impact of three factors that have
been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
criminal justice; 3) demand for harsher punishment for criminals. Below, we
discuss them in further detail.

* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
  According to the neighbours, he tried to break into a house but was
  immobilised and beaten by members of the community.[^control-exp02]

[^control-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade.

* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
  house but was immobilised and beaten by members of the community. **One of
  the residents who took part in the lynching said they had beaten the suspect
  because "the police never patrols the area"**.[^treat01-exp02]

[^treat01-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
nunca patrulha o local".**

* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial system is too slow and the perpetrator is on
  the street until the case is heard"**.[^treat02-exp02]

[^treat02-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
é muito lenta e os criminosos ficam soltos até o julgamento"**.

* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial punishment is not harsh
  enough"**.[^treat03-exp02]

[^treat03-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
da justiça não é dura o suficiente"**.

* You will be shown a news article. Please read it carefully. After you read
  the article, we will ask you one question about it.[^vig01-exp02]

[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por
favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
sobre ele.

* Do you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp02]

[^vig02-exp02]: In Portuguese: Você acha que o linchamento foi correto? Por
favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
discordar.

Table \ref{tab:exp02main} summarizes our results. As we see, none of the
treatment effects are statistically significant at conventional levels. This
suggests that institutional factors do not affect lynching support in our
sample.

\footnotesize
```{r exp02-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02 <- df1 %>%
  mutate(exp02_outcomes = coalesce(exp02_control, exp02_police,
                                   exp02_slow_justice, exp02_small_punishment),
         exp02_any_treat = case_when(!is.na(exp02_control) ~ "0",
                                     !is.na(exp02_police) ~ "1",
                                     !is.na(exp02_slow_justice) ~ "1",
                                     !is.na(exp02_small_punishment) ~ "1",
                                     TRUE ~ NA_character_),
         exp02_police_treat = case_when(!is.na(exp02_control) ~ "0",
                                        !is.na(exp02_police) ~ "1"),
         exp02_slow_justice_treat = case_when(!is.na(exp02_control) ~ "0",
                                              !is.na(exp02_slow_justice) ~ "1"),
         exp02_small_punishment_treat = case_when(!is.na(exp02_control) ~ "0",
                                                  !is.na(exp02_small_punishment) ~ "1"))

# Models
m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02main",
          title = "Experiment 02 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

>>>>

---
title: |
       | Supplementary Materials for "Vigilantism, Institutions, and Culture: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

[^freire]: School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <http://danilofreire.github.io>.

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, <davidskarbek@brown.edu>, <http://davidskarbek.com>.

@@

This appendix contains the `R` code required to replicate the results we
present in "_Vigilantism, Institutions, and Culture: Understanding Attitudes
towards Lynching in Brazil_". This file also includes the descriptive
statistics of our sample, the average marginal component effects (AMCEs) for
our conjoint experiment, and additional subgroup analyses for all three
experiments.

@@

# Load the dataset, remove unused rows and columns,
# and convert variable names to snake case
df <- read_csv("../data/data.csv") %>%
  clean_names() %>%
  mutate(response_id            = as.character(response_id),
         consent                = as.factor(q1),
         progress               = as.numeric(progress),
         finished               = as.factor(finished),
         age                    = as.numeric(q2),
         gender                 = as.factor(q3),
         race                   = as.factor(q4),
         education              = as.factor(q5),
         region                 = as.factor(q6),
         household_income       = as.factor(q7),
         ideology               = as.factor(q8),
         death_penalty          = as.factor(q9),
         previous_victim        = as.character(q10),
         previous_victim_text   = as.character(q10_text),
         views_police           = as.factor(q11),
         views_justice          = as.factor(q12),
         exp01_control          = as.numeric(q18),
         exp01_police           = as.numeric(q19),
         exp01_slow_justice     = as.numeric(q20),
         exp01_small_punishment = as.numeric(q21),
         exp03_control          = as.numeric(q22),
         exp03_constitution     = as.numeric(q23),
         exp03_rights           = as.numeric(q24),
         exp03_vendetta         = as.numeric(q25)) %>%
  slice(-1L) %>%
  select(-c(q1:q12, q18:q25)) %>%
  relocate(response_id, consent, progress, finished,
           location_latitude, location_longitude) %>%
  mutate(across(where(is.character), tolower)) %>%
  mutate(across(where(is.factor), tolower))

@@

In our first experiment, we analyze how respondents justify their preferences
towards extralegal violence. We assess the impact of three factors that have
been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
criminal justice; 3) demand for harsher punishment for criminals. Below, we
discuss them in further detail.

* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
  According to the neighbours, he tried to break into a house but was
  immobilised and beaten by members of the community.[^control-exp01]

[^control-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade.

* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
  house but was immobilised and beaten by members of the community. **One of
  the residents who took part in the lynching said they had beaten the suspect
  because "the police never patrols the area"**.[^treat01-exp01]

[^treat01-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
nunca patrulha o local".**

* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial system is too slow and the perpetrator is on
  the street until the case is heard"**.[^treat02-exp01]

[^treat02-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
é muito lenta e os criminosos ficam soltos até o julgamento"**.

* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial punishment is not harsh
  enough"**.[^treat03-exp01]

[^treat03-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
da justiça não é dura o suficiente"**.

* You will be shown a news article. Please read it carefully. After you read
  the article, we will ask you one question about it.[^vig01-exp01]

[^vig01-exp01]: In Portuguese: Uma notícia será apresentada para você. Por
favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
sobre ele.

* Do you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp01]

[^vig02-exp01]: In Portuguese: Você acha que o linchamento foi correto? Por
favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
discordar.

Table \ref{tab:exp01main} summarizes our results. As we see, none of the
treatment effects are statistically significant at conventional levels. This
suggests that institutional factors do not affect lynching support in our
sample.

\footnotesize
```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp01 <- df1 %>%
  mutate(exp01_outcomes = coalesce(exp01_control, exp01_police,
                                   exp01_slow_justice, exp01_small_punishment),
         exp01_any_treat = case_when(!is.na(exp01_control) ~ "0",
                                     !is.na(exp01_police) ~ "1",
                                     !is.na(exp01_slow_justice) ~ "1",
                                     !is.na(exp01_small_punishment) ~ "1",
                                     TRUE ~ NA_character_),
         exp01_police_treat = case_when(!is.na(exp01_control) ~ "0",
                                        !is.na(exp01_police) ~ "1"),
         exp01_slow_justice_treat = case_when(!is.na(exp01_control) ~ "0",
                                              !is.na(exp01_slow_justice) ~ "1"),
         exp01_small_punishment_treat = case_when(!is.na(exp01_control) ~ "0",
                                                  !is.na(exp01_small_punishment) ~ "1"))

# Models
m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01main",
          title = "Experiment 01 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

## Determinants of Baseline Levels

Here we estimate the effect of gender, race, and political ideology on
lynching support. We find that males, blacks, and mixed race individuals are
more likely to endorse lynchings when compared to females and whites,
respectively. Left and center-left voters, in contrast, show lower support for
lynchings when compared to centrists.

\footnotesize
```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp01_group <- df_exp01 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         ideology %in% c("Center", "Center-Left", "Center-Right",
                         "Left", "Right"))

m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_group)
m2 <- lm(exp01_outcomes ~ relevel(race, ref = "White"), data = df_exp01_group)
m3 <- lm(exp01_outcomes ~ relevel(ideology, ref = "Center"), data = df_exp01_group)
m4 <- lm(exp01_outcomes ~ gender + relevel(race, ref = "White") +
         relevel(ideology, ref = "Center"), data = df_exp01_group)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01baseline",
          title = "Experiment 01 -- Determinants of Baseline Levels of
          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Male", "Asian", "Black", "Mixed Race",
                               "Left", "Center-Left", "Center-Right", "Right"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

\footnotesize
```{r exp01-bart01, warning=F, error=F, message=F, cache=T}
df_exp01_het <- df_exp01 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))

df_exp01_police <- df_exp01_het %>%
  mutate(exp01_police_treat = as.numeric(exp01_police_treat)) %>%
  drop_na(exp01_police_treat)

# Gender
summary(bartc(exp01_outcomes, exp01_police_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Age
summary(bartc(exp01_outcomes, exp01_police_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp01_outcomes, exp01_police_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp01_outcomes, exp01_police_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp01_outcomes, exp01_police_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp01_outcomes, exp01_police_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp01_outcomes, exp01_police_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp01_police2 <- df_exp01_police %>% drop_na(previous_victim_dummy)
summary(bartc(exp01_outcomes, exp01_police_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_police2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp01_outcomes, exp01_police_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp01_outcomes, exp01_police_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))
```
\normalsize

\footnotesize
```{r exp01-bart02, warning=F, error=F, message=F, cache=T}
# Remove "Indigenous" and "Other" from `race` as they only
# have 1 observation each. The model cannot be estimated otherwise.
df_exp01_slow_justice <- df_exp01_het %>%
  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
  mutate(exp01_slow_justice_treat = as.numeric(exp01_slow_justice_treat)) %>%
  drop_na(exp01_slow_justice_treat)

# Gender
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Age
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp01_slow_justice2 <- df_exp01_slow_justice %>% drop_na(previous_victim_dummy)
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_slow_justice2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))
```
\normalsize

\footnotesize
```{r exp01-bart03, warning=F, error=F, message=F, cache=T}
df_exp01_small_punishment <- df_exp01_het %>%
  mutate(exp01_small_punishment_treat = as.numeric(exp01_small_punishment_treat)) %>%
  drop_na(exp01_small_punishment_treat)

# Gender
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Age
df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(age2)
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp01_small_punishment2,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(previous_victim_dummy)
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_small_punishment2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
              n.chains = 5L, seed = 144))
```
\normalsize

In our second experiment, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

@@

\footnotesize
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education)),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School"))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)

@@

\footnotesize
```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
                                   views_police == "Don't Know" ~ NA_character_,
                                   TRUE ~ as.character(views_police)),
         views_police2 = fct_relevel(views_police2, "Very Good", "Good",
                                     "Regular", "Bad", "Very Bad")) %>%
  drop_na(views_police2)
cjdt$Police <- factor(cjdt$views_police2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)

@@

\footnotesize
```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
                                    views_justice == "Don't Know" ~ NA_character_,
                                   TRUE ~ as.character(views_justice)),
         views_justice2 = fct_relevel(views_justice2, "Very Good", "Good",
                                      "Regular", "Bad", "Very Bad")) %>%
  drop_na(views_justice2)
cjdt$Judiciary <- factor(cjdt$views_justice2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)

@@

\footnotesize
```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles"}
dfmat <- df1 %>%
  select(q13_text, q14_text, q15_text, q16_text, q17_text) %>%
  gather() %>%
  corpus(text_field = "value") %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE,
         remove_symbol = TRUE) %>%
  dfm() %>%
  dfm_remove(., pattern = c(stopwords("pt", source = "snowball"),
                            "é", "ser"))

@@
